---
title: "Developing Data Products"
author: "Bidalika Kumari"
date: "22/07/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Application

#### To analyze the code you can go to https://github.com/Bidalika/shiny/tree/master/newapp
#### To see the shiny app you can go to 

## What is the function of this application ?

This application is ment to help you in 
visualisation of the ploing of the random data.

- It allows you to visualise the ploting of random 
number of points within a specified x and y range .
- You can use the slider to select the value of minimum 
and maximum of X Axis and Y Axis.
- And then you can check the check boxes according 
to your wish if you want to see or hide the x label 
or y label or the main title of the graph.

## R Output
The R code that is necessary before running any shiny application.
```{r echo=TRUE}
library(shiny)
```

## How will your output come ?

- First the default settings will be shown to you.
- You can edit the number of points to be ploted ,the range 
or x axis and y axis in which the points should be plotted.
- When you check the given boxes there then you can see the 
labels of x and y axis and the main title of the graph.
- You must click the button apply changes every time you 
change somethings.

## Thank You


